Notes for Week 12/7/19 - 12/29/19

### 2020-01-25 notes/weekly_notes/12.20.19.NotesForWeek.tex
updated weekly notes and project level notes

%%% Operators
\newcommand{\Tadj}{T^{\star}}
\newcommand{\Xsetive}{\mathrm{div}}
\newcommand{\Xsetif}{\mathop{}\!\mathrm{d}}
\newcommand{\gradient}{\mathcal{D}}
\newcommand{\Hessian}{\mathcal{D}^2}
\newcommand{\dotp}[2]{\langle #1, #2 \rangle}

@@

\section{Bounding the Roughness Functional in Expectation}

For an integer $\ell > 0$, we will say $K$ is a $2$nd-order kernel if it is bounded and compactly supported on $B(0,1)$ and additionally
\begin{equation*}
\int K(z) = 1 ~~\textrm{and}~~\int z K(z) = 0
\end{equation*}
That $K$ be a $2$nd-order kernel is crucial for $L_n$ to act as a $2$nd-order differential operator, and for $R_{s,n}$ to scale at the proper rate.

@@

@@

@@

When all indices $\ell,k,i$ and $j$ are distinct, by Lemma~\ref{lem:leading_term} there exists some $f_{s-1} \in C^1(L)$ such that
\begin{align*}
\Ebb(d_iD_kf(x_j)d_iD_{\ell}f(x_j)K_r(x_i,x_j)) & = \Ebb\biggl(\Bigl(d_i\bigl(O(r^{s-1})\cdot f_{s - 1} + O(r^s)\bigr)\Bigr)^2K_r(x_i,x_j)\biggr) \\
& = O(r^{2s - 2})\Ebb\Bigl(\bigl(d_if_{s-1}(x_j))\bigr)^2K_{r}(x_i,x_j)\Bigr) + O(r^{2s - 1})\Ebb\bigl(D_if_{s - 1}(x_j)\bigr)+ O(r^{2s})
\end{align*}
where the second equality follows from the linearity of the difference operator. Then since $f_{s-1} \in C^1(L)$, we have $\Ebb(D_if_{s-1}(x_j)) = O(r)$, and
\begin{equation*}
\Ebb\Bigl(\bigl(d_if_{s-1}(x_j))\bigr)^2K_{r}(x_i,x_j)\Bigr) = \Ebb\Bigl(\bigl(O(r)\bigr)^2K_{r}(x_i,x_j)\Bigr) = O(r^2),
\end{equation*}
establishing $\Ebb(d_iD_kf(x_j)d_iD_{\ell}f(x_j)K_r(x_i,x_j)) = O(r^{2s})$ as claimed.
\section{Auxiliary Results.}
\begin{lemma}
	\label{lem:difference_operator_taylor}
	When $f \in C^s(L)$, for any $k \in [n]$ 
	\begin{equation*}
	D_kf(x) = \left(\sum_{r = 1}^{s - 1} (x_k - x)^r f^{(r)}(x) + O((x_k - x)^{s})\right) \cdot K_r(x_k,x)
	\end{equation*}
\end{lemma}

@@

	We will prove by induction on $q$ in the case where $d = 1$. The When $q = 1$ and $k \in [n]$, by taking Taylor expansions of $f$ and $p$, we obtain
	\begin{align}
	\nonumber 
	\Ebb(D_kf(x)) & = \sum_{\ell = 1}^{s - 1} f^{(\ell)}(x) \int (z - x)^{\ell} K_r(z,x) p(z) dz + O(r^s) \\ 
	& = \sum_{\ell = 1}^{s - 1} \sum_{a = 0}^{s - 1} f^{(\ell)}(x) p^{(a)}(x) \underbrace{\int(z - x)^{\ell + a} K_r(z,x) dz}_{:=I_{t + a}} + O(r^s) \label{eqn:leading_term_pf1}
	\end{align}
	Since $K$ is a $2$nd-order kernel, $I_{1} = 0$ and $I_t = O(r^{t})$ for $t \geq 2$.  Additionally, when $\ell + a \leq s - 1$, we have that $f^{(\ell)}p^{(a)} \in C^{\min\{s - \ell, s - 1 - a\}} \subseteq C^{s - (\ell + a)}$, and $\abs{f^{(\ell)}p^{(a)}} \leq L^2$ for any $\ell$ and $a$. We can therefore simplify~\eqref{eqn:leading_term_pf1} by combining all terms where $\ell + a = t$, obtaining
	\begin{equation}
	\label{eqn:leading_term_pf2}
	\Ebb(D_kf(x)) = \sum_{t = 1}^{s - 1} f_t(x) I_t + O(r^s) = \sum_{t = 2}^{s - 1} f_t(x) I_t + O(r^s),
	\end{equation}
	which establishes~\eqref{eqn:leading_term} in the base case.

@@

>>>>

%%% Operators
\newcommand{\Tadj}{T^{\star}}
\newcommand{\Xsetive}{\mathrm{div}}
\newcommand{\Xsetif}{\mathop{}\!\mathrm{d}}
\newcommand{\gradient}{\nabla}
\newcommand{\Hessian}{\mathcal{D}^2}
\newcommand{\dotp}[2]{\langle #1, #2 \rangle}
\newcommand{\deriv}{\mathcal{D}}

@@

\section{Bounding the Roughness Functional when $f$ is Holder}

For an integer $\ell > 0$, we will say $K$ is a $2$nd-order kernel if it is compactly supported on $B(0,1)$, uniformly bounded $\abs{K(x)} \leq K_{\max}$ for all $x \in B(0,1)$, and additionally
\begin{equation*}
\int K(z) = 1 ~~\textrm{and}~~\int z K(z) = 0
\end{equation*}
That $K$ be a $2$nd-order kernel is crucial for $L_n$ to act as a $2$nd-order differential operator, and for $R_{s,n}$ to scale at the proper rate.

@@

\section{Bounding the Roughness Functional when $f$ is Sobolev}
Suppose $f$ is assumed to belong to the Sobolev space $W_d^{s,2}(\mathcal{X})$, and have small semi-norm in this space, rather than belonging to the Holder space $C_d^{s}(\Xset)$ and having small Holder norm. Can we still prove--possibly up to constants--the same bound on the expected graph semi-norm of $f$? Before answering this question, we review the definition of Sobolev spaces and their associated norms.

\subsection{Sobolev spaces}

For a given $s > 0$, the Sobolev space $W_d^{s,2}(\mathcal{X})$ consists of all functions $f \in \mathcal{L}^2(\mathcal{X})$ such that for each $\alpha = (\alpha_1,\ldots,\alpha_d)$ with $\abs{\alpha} := \sum_{i = 1}^{d} \alpha_i \leq s$, the weak derivative $D^{\alpha}f$ belongs to $\mathcal{L}^2(\mathcal{X})$. The Sobolev $\{s,2\}$ semi-norm is then 
\begin{equation*}
[f]_{W_d^{s,2}(\mathcal{X})} = \left(\sum_{\abs{\alpha} = s} \int_{\Xset} \abs{D^{\alpha}f}^2 \,dx\right)^{1/2}
\end{equation*}
and the Sobolev $\{s,2\}$ norm is 
\begin{equation*}
\norm{f}_{W_d^{s,2}(\mathcal{X})}^2 = \left(\sum_{q = 1}^{s} [f]_{W_d^{s,2}(\mathcal{X})}^2\right)^{1/2}.
\end{equation*}
For a $R > 0$, the corresponding ball is $W_d^{s,2}(\Xset; R) = \set{f: \norm{f}_{W^{s,2}(\Xset)} \leq R}$.

\subsection{Bounds on the graph semi-norm}

Under largely the same conditions as Lemma~\ref{lem:roughness_functional_expectation}, we have that the roughness functional $R_{s,n}(f)$ is (up to constants), no greater than the Sobolev norm $\norm{f}_{W_d^{1,2}(\mathcal{X})}$.
\begin{lemma}
	\label{lem:roughness_functional_expectation_sobolev}
	Let $\Xset$ be a Lipschitz domain. Suppose that $f \in W^{s,2}(\Xset)$, and further that $p \in C^{s-1}(\Xset;p_{\max})$ for some constant $p_{\max}$. Then for any $2$nd-order kernel $K$ and any $n^{-1/(2(s - 1) + d)} \leq r(n) \leq 1$, for sufficiently large $n$ the expected graph Sobolev seminorm is upper bounded
	\begin{equation}
	\label{eqn:roughness_functional_expectation_sobolev}
	\Ebb\bigl[R_{s,n}(f)\bigr] \leq c \cdot \norm{f}_{W_d^{s,2}(\Xset)}
	\end{equation}
	for some constant $c$ which may depend on $s$, $p_{\max}$, $K_{\max}$, $d$ and $\Xset$, but not on $f$, $r$ or $n$.
\end{lemma}

Note that the bound~\eqref{eqn:roughness_functional_expectation_sobolev} involves, on the right hand side, the norm $\norm{f}_{W_d^{s,2}(\Xset)}$ as opposed to the seminorm $[f]_{W_d^{s,2}(\Xset)}$. To better understand this, consider the following operator
\begin{equation*}
L_rf(x) = \frac{1}{r^2}\int (f(z) - f(x))K_r(z,x) \,dP(x)
\end{equation*} 
The operator $L_r$ is the expectation of the graph Laplacian, in the sense that $\Ebb(L_nf(x)) = L_rf(x)$, and so it makes sense that the behavior of the associated seminorm $\dotp{L_r^sf}{f}$ is related to the behavior of $\dotp{L_n^sf}{f}$. However, for any $s$ the seminorm $\dotp{L_r^sf}{f}$ assigns zero length only to constant functions $f$. As a one-dimensional example, if $s = 2$, and $f(x) = c \cdot x$ for $c$ large, the seminorm $\dotp{L_r^sf}{f}$ will also be quite large, despite the fact that the second derivative $f'' = 0$.

To be clear, $\Ebb[\dotp{L_n^sf}{f}] \neq \dotp{L_r^sf}{f}$, and bounding the former turns out to be non-trivial. The proof of Lemma~\ref{lem:roughness_functional_expectation_sobolev} relies on Lemma~\ref{lem:expected_difference_operators_sobolev}.

\begin{lemma}
	\label{lem:expected_difference_operators_sobolev}
	Let $\Xset$ be a Lipschitz domain, and suppose $f \in W_d^{s,2}(\Xset)$ for some $s \in \mathbb{N}_{+}$. Let $q = s/2$ when $s$ is even, and $q = (s - 1)/2$ when $s$ is odd. For any indices $k = (k_1,\ldots,k_q)$ and $\ell = (\ell_1,\ldots,\ell_q)$, we have
	\begin{equation}
	\label{eqn:expected_difference_operators_sobolev_1}
	\Ebb(D_kf(x_i) D_\ell f(x_i)) =
	\begin{cases*}
	O(r^{2s}) \cdot \norm{f}_{W_d^{s,2}(\Xset)}^2, & ~~\textrm{if all indices are distinct} \\
	O(r^{2} r^{d(\abs{k \cup \ell \cup i} - (2q + 1))})\cdot [f]_{W_d^{1,2}(\Xset)}^2, & ~~\textrm{otherwise}~ 
	\end{cases*}
	\end{equation}
	Additionally, we have
	\begin{equation}
	\label{eqn:expected_difference_operators_sobolev_2}
	\Ebb(d_iD_kf(x_j) d_iD_\ell f(x_j)) =
	\begin{cases*}
	O(r^{2s}) \cdot \norm{f}_{W_d^{s,2}(\Xset)}^2, & ~~\textrm{if all indices are distinct} \\
	O(r^{2} \cdot r^{d(\abs{k \cup \ell \cup i \cup j} - (2q + 2))}) \cdot [f]_{W_d^{1,2}(\Xset)}^2, & ~~\textrm{otherwise}~ 
	\end{cases*}
	\end{equation}
\end{lemma}

The lower bound on $r(n)$ in Lemma~\ref{lem:roughness_functional_expectation_sobolev} is needed to ensure the leading term in~\eqref{eqn:expected_difference_operators_sobolev_1} (or~\eqref{eqn:expected_difference_operators_sobolev_2}), where all indices are distinct, dominates the lower-order terms, where indices are repeated.

@@

\subsection{Proof of Lemma~\ref{lem:expected_difference_operators_sobolev}}

We first prove the desired bound in the case when some indices are repeated, and then the desired bound in the case when all indices are distinct.

\subsubsection{Repeated indices.}

Since the proofs of~\eqref{eqn:expected_difference_operators_sobolev_1} and~\eqref{eqn:expected_difference_operators_sobolev_2} are essentially the same for the case where some index is repeated, we will assume without loss of generality that $s$ is even. Let $k,\ell \in [n]^q$ be index vectors for $q = s/2$.

When at least one index is repeated, we obtain a sufficient upper bound by reducing the problem of upper bounding the iterated difference operator to that of upper bounding a single difference operator. Letting $k = (k_1,\ldots,k_q)$, we can show by induction that the absolute value of the iterated difference operator $\abs{D_kf(x_i)}$ is upper bounded by
\begin{equation*}
\abs{D_kf(x_i)} \leq \left(\frac{2K_{\max}}{r^d}\right)^{q-1} \sum_{h \in k \cup i} \abs{D_{k_q}f(x_h)} \cdot \1\{G_{n,r}[X_{k \cup i}]~\textrm{is a connected graph} \}.
\end{equation*}
Therefore,
\begin{align}
\abs{D_kf(x_i)} \abs{D_{\ell}f(x_i)} & \leq \left(\frac{2K_{\max}}{r^d}\right)^{2(q - 1)} \sum_{h,j \in k \cup \ell \cup i} \abs{D_{k_q}f(x_h)} \cdot \abs{D_{\ell_q}f(x_j)} \cdot \1\{G_{n,r}[X_{k \cup i}], G_{n,r}[X_{\ell \cup i}]~\textrm{are connected graphs.} \} \nonumber \\
& =  \left(\frac{2K_{\max}}{r^d}\right)^{2(q - 1)} \sum_{h,j \in k \cup \ell \cup i} \abs{D_{k_q}f(x_h)} \cdot \abs{D_{\ell_q}f(x_j)} \cdot \1\{G_{n,r}[X_{k \cup \ell \cup i}] ~\textrm{is a connected graph.} \} \label{eqn:expected_difference_operators_sobolev_pf0}
\end{align}

We now break our analysis into three cases, based on the number of distinct indices in $k_q,\ell_q,h,j$.

\paragraph{Case 1: Two distinct indices.}
Let $k_q = \ell_q = i$, and $h = j$. Using the law of iterated expectation, we obtain
\begin{align*}
\Ebb \left[\left(D_{i}f(x_j)\right)^2 \cdot \1\{G_{n,r}[X_{k \cup \ell \cup i}] ~\textrm{is connected} \}\right] &= \Ebb \left[\left(D_{i}f(x_j)\right)^2 \cdot \Pbb\left[\{G_{n,r}[X_{k \cup \ell \cup i}] ~\textrm{is connected} \} |x_i,x_j\right]\right] \\
& = O(r^{(\abs{k \cup \ell \cup i} - 2)d}) \cdot \Ebb\left[(D_i(f(x_j))^2\right] \\
& = O(r^{(\abs{k \cup \ell \cup i} - 3)d}) \cdot \Ebb\left[(d_if(x_j))^2K_r(x_i,x_j)\right] \\
& = O(r^{(\abs{k \cup \ell \cup i} - 3)d + 2}) [f]_{W^{1,2}(\Xset)}^2
\end{align*}
where the last equality follows from Lemma~\ref{lem:expected_first_order_seminorm}.
\paragraph{Case 2: Three distinct indices.}
Let $k_q = \ell_q = i$, for some $i \neq j \neq h$. Using the law of iterated expectation, we obtain
\begin{align}
\Ebb & \left[\abs{D_{i}f(x_j)} \cdot \abs{D_if(x_h)} \cdot \1\{G_{n,r}[X_{k \cup \ell \cup i}] ~\textrm{is connected} \}\right] \\
& = \Ebb \left[\abs{D_{i}f(x_j)} \cdot \abs{D_if(x_h)} \cdot \Pbb\left[\{G_{n,r}[X_{k \cup \ell \cup i}] ~\textrm{is connected} \} |x_i,x_j,x_h\right]\right] \nonumber \\
& = O(r^{(\abs{k \cup \ell \cup i} - 3)d}) \cdot \Ebb\left[\abs{D_{i}f(x_j)} \cdot \abs{D_if(x_h)} \right]. \label{eqn:expected_difference_operators_sobolev_pf1}
\end{align}
It remains to upper bound $\Ebb\left[\abs{D_{i}f(x_j)} \cdot \abs{D_if(x_h)} \right]$, which we rewrite as
\begin{align*}
\Ebb\left[\abs{D_{i}f(x_j)} \cdot \abs{D_if(x_h)} \right] & = \int \int \int \abs{f(z) - f(x)} \abs{f(z) - f(y)} K_r(z,y) K_r(z,x) \,dP(x) \,dP(y) \,dP(x) \\
& = \int \left[\int \abs{f(z) - f(x)} K_r(z,x) \,dP(x)\right]^2 \,dP(z) \\
& \leq p_{\max}^3 \int_{\Xset} \left[\int_{\Xset} \abs{f(z) - f(x)} K_r(z,x) \,dx\right]^2 \,dz
\end{align*}
By the argument set out in Section~\ref{subsec:proof_of_lemma_graph_Sobolev_seminorm_1}, we may assume without loss of generality that there exists an extension $g \in C_d^{\infty}(\Xset) \cap W_d^{1,2}(\Rd)$ such that $[g]_{W_d^{1,2}(\Rd)} \leq c [f]_{W_d^{1,2}(\Xset)}$. Then, by a similar series of steps as in Section~\ref{subsec:proof_of_lemma_graph_Sobolev_seminorm_1}, we obtain
\begin{align*}
\int_{\Xset} \abs{f(z) - f(x)} K_r(z,x) \,dx & \leq \int_{\Rd} \abs{g(z) - g(x)} K_r(z,x) \,dx \\
& = \int_{\Rd} \abs{\int_{0}^{1} \dotp{\nabla g(x + t(z - x))}{z - x} \,dt} K_r(z,x) \,dx \\
& \leq \int_{\Rd} \int_{0}^{1} \norm{\nabla g(x + t(z - x))}\cdot\norm{z - x} \,dt K_r(z,x) \,dx \\
& \leq r \int_{\Rd} \int_{0}^{1} \norm{\nabla g(x + t(z - x))} \,dt K_r(z,x) \,dx \\
& \leq r \frac{K_{\max}}{r^d} \int_{B(z,r)} \int_{0}^{1} \norm{\nabla g(x + t(z - x))} \,dt  \,dx \\
& \leq r K_{\max} \int_{B(0,1)} \int_{0}^{1} \norm{\nabla g(x - try)} \,dt  \,dy,
\end{align*}
and as a result, 
\begin{equation*}
p_{\max}^3 \int_{\Xset} \left[\int_{\Xset} \abs{f(z) - f(x)} K_r(z,x) \,dx\right]^2 \,dz \leq c\cdot p_{\max}^3 r^2 K_{\max}^3 [f]_{W_d^{1,2}(\Rd)}^2 = O(r^2)\cdot [f]_{W_d^{1,2}(\Xset)}^2
\end{equation*}
Plugging back into~\eqref{eqn:expected_difference_operators_sobolev_pf1}, we have that $\Ebb \left[\abs{D_{i}f(x_j)} \cdot \abs{D_if(x_h)} \cdot \1\{G_{n,r}[X_{k \cup \ell \cup i}] ~\textrm{is connected} \}\right] = O(r^{d(\abs{k \cup \ell \cup i} - 3) + 2}) \cdot [f]_{W_d^{1,2}(\Xset)}^2$.

\paragraph{Case 3: Four distinct indices.}
Using the law of iterated expectation, we find that
\begin{align*}
\Ebb[ &\abs{D_{k_q}f(x_i)}{\abs{D_{\ell_q}f(x_j)}} \1\{G_{n,r}[X_{k \cup \ell \cup i}] ~\textrm{is connected} \}] \\
& = \Ebb[\abs{D_{k_q}f(x_i)}{\abs{D_{\ell_q}f(x_j)}} \Pbb(G_{n,r}[X_{k \cup \ell \cup i}] ~\textrm{is connected}|x_i,x_j,x_{k_q},x_{\ell_q})] \\
& = O(r^{d(\abs{k \cup \ell \cup i} - 4)}) \cdot \Ebb\bigl[\abs{D_{k_q}f(x_i)}\cdot{\abs{D_{\ell_q}f(x_j)}}\cdot\1\{\norm{x_i - x_j} \leq (2q + 1)r\}\bigr] 
\end{align*}
Replacing $f$ by a smooth extension $g \in C^{\infty}(\Xset) \cap W_d^{1,2}(\Rd)$, we rewrite the expectation as an integral,
\begin{align*}
\Ebb\bigl[& \abs{D_{k_q}f(x_i)}\cdot{\abs{D_{\ell_q}f(x_j)}}\cdot\1\{\norm{x_i - x_j} \leq (2q + 1)r\}\bigr] \\
& \leq p_{\max}^4 \int_{\Xset^4} \abs{g(x) - g(y)} \abs{g(u) - g(v)} K_r(x,y) K_r(u,v) \1\{\norm{y - v} \leq (2q + 1)r\} \,dy \,dx \,du \,dv
\end{align*}
By substituting $z_1 = (y - v)/r$, $z_2 = (u - v)/r$, and $z_3 = (x - y)/r = (x - v)/r + z_1$, we can simplify the integral in the previous display,
\begin{align*}
\int_{\Xset^4} & \abs{g(x) - g(y)} \abs{g(u) - g(v)} K_r(x,y) K_r(u,v) \1\{\norm{y - v} \leq (2q + 1)r\} \,dy \,dx \,du \,dv \\
& \leq K_{\max}^2 r^d \int_{\Xset} \int_{[B(0,1)]^3} \abs{g\bigl((z_3 + z_1)r + v\bigr) - g(z_1r + v)} \bigl|g(z_2r + v) - g(v)\bigr| \,dz_1 \,dz_2 \,dz_3 \,dv \\
& \leq  K_{\max}^2 r^{d + 2} \int_{[B(0,1)]^3} \int_{[0,1]^2} \int_{\Xset} \norm{\nabla g(t z_3 r + z_1r + v)} \cdot \norm{\nabla g(t z_2 r + v)} \,dv \,dt_1 \,dt_2 \,dz_1 \,dz_2 \,dz_3 \\
& \leq c \nu_d^3 K_{\max}^2 r^{d + 2} [f]_{W_{d}^{1,2}(\Xset)}^2.
\end{align*}
Therefore $\Ebb[ \abs{D_{k_q}f(x_i)}{\abs{D_{\ell_q}f(x_j)}} \1\{G_{n,r}[X_{k \cup \ell \cup i}] ~\textrm{is connected} \}] = O(r^{d(\abs{k \cup \ell \cup i} - 3) + 2})\cdot [f]_{W_d^{1,2}(\Xset)}^2$.

Since we obtain the same scaling in each case, plugging this back in to~\eqref{eqn:expected_difference_operators_sobolev_pf0} we have that for any $k, \ell \in [n]^q$
\begin{equation*}
\Ebb\bigl[\abs{D_kf(x_i)} \abs{D_\ell f(x_i)}\bigr] = O(r^{d(\abs{k \cup \ell \cup i} - (2q + 1)) + 2}) \cdot [f]_{W_d^{1,2}(\Xset)}^2.
\end{equation*}

\subsubsection{All indices distinct.}

We first show the desired result when $s$ is even, and then when $s$ is odd. In either case, since $\Xset$ is a Lipschitz domain, there exists an extension $g \in W^{s,2}(\Rd)$ such that $\norm{g}_{W^{s,2}(\Rd)} \leq c \norm{f}_{W^{s,2}(\Xset)}$, and $g = f$ a.e in $\Xset$. Further, there exists a sequence of smooth approximations $(g_m) \subset C^{\infty}(\Rd)$, such that
\begin{equation*}
\norm{g_m - g}_{W^{s,2}(\Rd)} \to 0.
\end{equation*}

\paragraph{$s$ even.}

By the law of iterated expectation, we have
\begin{align*}
\Ebb\bigl[D_kf(x_i)D_kf(x_j)\bigr] = \Ebb\bigl[D_kg(x_i)D_kg(x_j)\bigr] & = \Ebb\Bigl[\bigl(\Ebb[D_kg(x_i)|x_i]\bigr)^2\Bigr] \\
& \leq 2\Ebb\Bigl[\bigl(\Ebb[D_kg_m(x_i)|x_i]\bigr)^2\Bigr] + \Ebb\Bigl[\bigl(\Ebb[D_k(g - g_m)(x_i)|x_i]\bigr)^2\Bigr] \\
& \leq 2\Ebb\Bigl[\bigl(\Ebb[D_kg_m(x_i)|x_i]\bigr)^2\Bigr] + \left(\frac{2K_{\max}}{r^d}\right)^q \norm{g - g_m}_{\Leb^2(\Rd)}^2.
\end{align*}
By Lemma~\ref{lem:leading_term_sobolev}, we have that $\Ebb[D_kg_m(x_i)|x_i]\bigr)^2 = O(r^{2s})\cdot [f_s(x)]^2$ for some $f_s \in \Leb^2(\Rd)$ which satisfies $\norm{f_s}_{\Leb^2(\Rd)} \leq c \norm{g_m}_{W^{s,2}(\Rd)}$ for some constant $c$ which does not depend on $g_m$. Along with the previous display, this implies
\begin{equation*}
\Ebb\bigl[D_kf(x_i)D_kf(x_j)\bigr] \leq O(r^{2s}) \norm{g_m}_{W^{s,2}(\Rd)}^2 + \left(\frac{2K_{\max}}{r^d}\right)^q \norm{g - g_m}_{\Leb^2(\Rd)}^2,
\end{equation*}
and taking the limit of the right hand side as $m \to \infty$ we have $\Ebb\bigl[D_kf(x_i)D_kf(x_j)\bigr] \leq O(r^{2s})\cdot\norm{f}_{W^{s,2}(\Rd)}^2$.

\paragraph{$s$ odd.}

By the law of iterated expectation, we have
\begin{align*}
\Ebb[d_iD_kg_m(x_j)d_iD_{\ell}g_m(x_j)K_r(x_i,x_j)] & = \Ebb\biggl[\Bigl(d_i\bigl(\Ebb(D_kf)\bigr)(x_j)\Bigr)^2K_r(x_i,x_j)\biggr] \\
& = \Ebb\biggl[\Bigl(d_i\bigl(I_{s - 1}\cdot f_{s - 1} + O(r^s)f_s(x_j)\bigr)(x_j)\Bigr)^2K_r(x_i,x_j)\biggr].
\end{align*}
where the latter equality follows from Lemma~\ref{lem:leading_term_sobolev}. Here $I_{s - 1}, f_{s -1}$ and $f_s$ satisfy the conclusions of that Lemma, namely that $\abs{I_{s - 1}} \leq r^{s - 1}$, $f_{s - 1}$ and $f_s \in C^{\infty}(\Rd)$, and
\begin{equation*}
\norm{f_{s - 1}}_{W^{1,2}(\Rd)}, \norm{f_s}_{\Leb^2(\Rd)} \leq c \norm{g_m}_{W^{s,2}(\Rd)}.
\end{equation*}
By the linearity and boundedness of the difference operator $d_i$, we have
\begin{align*}
\Ebb\biggl[\Bigl(d_i\bigl(I_{s - 1}\cdot f_{s - 1} + O(r^s)f_s(x_j)\bigr)(x_j)\Bigr)^2K_r(x_i,x_j)\biggr] & = \Ebb\biggl[\Bigl(I_{s - 1} d_if_{s - 1}(x_j) + O(r^s)f_s(x_j)\Bigr)^2K_r(x_i,x_j)\biggr] \\
& \leq 2I_{s - 1}^2 \Ebb\Bigl[\bigl(d_if_{s-1}(x_j)\bigr)^2K_r(x_i,x_j)\Bigr] + O(r^{2s})\Ebb\Bigl[f_s(x_j)^2\Bigr] \\
& = O(r^{2(s - 1)})\Ebb\Bigl[\bigl(d_if_{s-1}(x_j)\bigr)^2K_r(x_i,x_j)\Bigr] + O(r^{2s}) \norm{g_m}_{W^{s,2}(\Rd)}^2 \\
& \leq O(r^{2s}) \norm{g_m}_{W^{s,2}(\Rd)}^2
\end{align*}
where the last inequality follows from Lemma~\ref{lem:expected_first_order_seminorm}.
By similar arguments to the case where $s$ is even, we can show that this estimate holds (up to constants) when $g_m$ is replaced by $f$, establishing the claim.

@@

When all indices $\ell,k,i$ and $j$ are distinct, by Lemma~\ref{lem:leading_term} there exists some $f_{s-1} \in C^1(L)$ such that
\begin{align*}
\Ebb(d_iD_kf(x_j)d_iD_{\ell}f(x_j)K_r(x_i,x_j)) & = \Ebb\biggl(\Bigl(d_i\bigl(O(r^{s-1})\cdot f_{s - 1} + O(r^s)\bigr)\Bigr)^2K_r(x_i,x_j)\biggr) \\
& = O(r^{2s - 2})\Ebb\Bigl(\bigl(d_if_{s-1}(x_j))\bigr)^2K_{r}(x_i,x_j)\Bigr) + O(r^{2s - 1})\Ebb\bigl(D_if_{s - 1}(x_j)\bigr)+ O(r^{2s})
\end{align*}
where the second equality follows from the linearity of the difference operator. Then since $f_{s-1} \in C^1(L)$, we have $\Ebb(D_if_{s-1}(x_j)) = O(r)$, and
\begin{equation*}
\Ebb\Bigl(\bigl(d_if_{s-1}(x_j))\bigr)^2K_{r}(x_i,x_j)\Bigr) = \Ebb\Bigl(\bigl(O(r)\bigr)^2K_{r}(x_i,x_j)\Bigr) = O(r^2),
\end{equation*}
establishing $\Ebb(d_iD_kf(x_j)d_iD_{\ell}f(x_j)K_r(x_i,x_j)) = O(r^{2s})$ as claimed.

\section{Auxiliary Results.}
\begin{lemma}
	\label{lem:difference_operator_taylor}
	When $f \in C^s(L)$, for any $k \in [n]$ 
	\begin{equation*}
	D_kf(x) = \left(\sum_{r = 1}^{s - 1} (x_k - x)^r f^{(r)}(x) + O((x_k - x)^{s})\right) \cdot K_r(x_k,x)
	\end{equation*}
\end{lemma}

@@

	We will prove by induction on $q$ in the case where $d = 1$. When $q = 1$ and $k \in [n]$, by taking Taylor expansions of $f$ and $p$, we obtain
	\begin{align}
	\nonumber 
	\Ebb(D_kf(x)) & = \sum_{\ell = 1}^{s - 1} f^{(\ell)}(x) \int (z - x)^{\ell} K_r(z,x) p(z) dz + O(r^s) \\ 
	& = \sum_{\ell = 1}^{s - 1} \sum_{a = 0}^{s - 1} f^{(\ell)}(x) p^{(a)}(x) \underbrace{\int(z - x)^{\ell + a} K_r(z,x) dz}_{:=I_{t + a}} + O(r^s) \label{eqn:leading_term_pf1}
	\end{align}
	Since $K$ is a $2$nd-order kernel, $I_{1} = 0$ and $I_t = O(r^{t})$ for $t \geq 2$.  Additionally, when $\ell + a \leq s - 1$, we have that $f^{(\ell)}p^{(a)} \in C^{\min\{s - \ell, s - 1 - a\}} \subseteq C^{s - (\ell + a)}$, and $\abs{f^{(\ell)}p^{(a)}} \leq L^2$ for any $\ell$ and $a$. We can therefore simplify~\eqref{eqn:leading_term_pf1} by combining all terms where $\ell + a = t$, obtaining
	\begin{equation}
	\label{eqn:leading_term_pf2}
	\Ebb(D_kf(x)) = \sum_{t = 1}^{s - 1} f_t(x) I_t + O(r^s) = \sum_{t = 2}^{s - 1} f_t(x) I_t + O(r^s),
	\end{equation}
	which establishes~\eqref{eqn:leading_term} in the base case.

@@

The following Lemma establishes a result analogous to Lemma~\ref{lem:leading_term} when the function $f$ and density $p$ are assumed to be bounded in Sobolev, rather than Holder, norm. We use multiindex notation to represent higher order partial derivatives and polynomials. For $\alpha \in [\mathbb{N}]^d$, and $x,z \in \Rd$ we write
\begin{equation*}
\abs{\alpha} = \alpha_1 + \cdots + \alpha_d,~~ f^{(\alpha)} = \frac{\partial^{\abs{\alpha}}f}{\partial x_{\alpha_1}\ldots \partial x_{\alpha_q}},~~ (x - z)^{\alpha} := (x_{\alpha_1} - z_{\alpha_1})\cdots(x_{\alpha_d} - z_{\alpha_d})
\end{equation*}
\begin{lemma}
	\label{lem:leading_term_sobolev}
	Let $k \in [n]^q$ for some $q \geq 1$. Suppose that $f \in W_d^{s,2}(\Rd) \cap C_d^{\infty}(\Rd)$ and $p \in C_d^{s - 1}(\Rd;p_{\max})$, and that $K_r$ is a second order kernel. Then there exist
	\begin{itemize}
		\item functions $f_{\ell}, \ell = 2q,\ldots,s$ satisfying $f_{\ell} \in W_d^{s - \ell,2}(\Rd) \cap C_d^{\infty}(\Rd)$ and
		\begin{equation*}
		\norm{f_{\ell}}_{W_d^{s - \ell,2}(\Rd)} \leq c \norm{f}_{W_d^{s,2}(\Rd)}
		\end{equation*}
		for some constant $c$ which depends only on $d$, $\Xset$ and $p_{\max}$, and 
		\item constants $I_{\ell},\ell = 2q,\ldots,s$ which depend only on $K(\cdot)$ satisfying $\abs{I_{\ell}} \leq r^{\ell}$,
	\end{itemize}
	such that
	\begin{equation}
	\label{eqn:leading_term_sobolev}
	\Ebb(D_kf(x)) =
	\begin{cases*}
	\sum_{\ell = 2q}^{s - 1} I_{\ell} \cdot f_{\ell}(x) +  O(r^{s}) \cdot f_{s}(x),~~& \textrm{if $2q < s$} \\
	O(r^{s}) \cdot f_{s}(x),~~& \textrm{if $2q \geq s$}
	\end{cases*}
	\end{equation}
	The $O(\cdot)$ term may depend on $s, K_{\max}$ and $p_{\max}$, but does not depend on $f$.
\end{lemma}
\begin{proof}	
	We proceed by induction on $q$. 
	\paragraph{Base case.}
	We begin with the base case of $q = 1$. Since $f$ and $p$ are smooth, they both admit Taylor expansions of the following form for all $x,z \in \Rd$:
	\begin{align*}
	f(z) & = \sum_{\abs{\alpha} < s} \frac{f^{(\alpha)}(x)}{\alpha!} (x - z)^{\alpha} + \frac{\abs{\alpha}}{\alpha!}\sum_{\abs{\alpha} = s} (x - z)^{\alpha} \int_{0}^{1}(1 - t)^{s - 1} f^{(\alpha)}(x + t(z - x)) \,dt\\
	p(z) & = \sum_{\abs{\beta} < s  - 1} \frac{p^{(\beta)}(x)}{\beta!} (x - z)^{\beta} + O((x - z)^{s - 1})
	\end{align*}
	where $f^{(\alpha)} \in W^{s - \abs{\alpha},2}(\Rd) \cap C^{\infty}(\Rd)$ additionally satisfies
	\begin{equation*}
	\norm{f^{(\alpha)}}_{W^{s - \abs{\alpha},2}(\Rd)} \leq \norm{f}_{W^{s,2}(\Rd)}
	\end{equation*}
